Hydra Battles and Cie

### 2021-08-08 doc/part-hydras.tex
converting chapter 4 to Alectryon (start)

\begin{Coqsrc}
Inductive T1 : Set  :=
| zero : T1
| ocons : T1 -> nat -> T1 -> T1.
\end{Coqsrc}

\paragraph{Remark}
The name \texttt{T1} we gave to this data-type  is proper to this development and refers
to a hierarchy of ordinal notations. For instance, in Library \href{../theories/html/hydras.Gamma0.T2.html}{Gamma0.T2},  the following type is used to represent ordinals strictly less than \(\Gamma_0\),  in Veblen normal form (see also~\cite{schutte}).
\noindent
\begin{Coqsrc}
Inductive T2 : Set :=
  zero : T2
| gcons : T2 -> T2 -> nat -> T2 -> T2.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example alpha_0 : T1 :=
  ocons (ocons (ocons zero 0 zero)
               0
               zero)
        0
       (ocons (ocons zero 2 zero)
              4
              (ocons zero 1 zero)).
\end{Coqsrc}

@@

\begin{Coqsrc}
Notation one := (ocons zero 0 zero).

Notation FS n := (ocons zero n zero).
\end{Coqsrc}

@@

\begin{Coqsrc}
Definition fin (n:nat) : T1 := 
    match n with 0 => zero | S p => FS p end.

Coercion fin  : nat >-> T1.

Example ten : T1 := 10.   
\end{Coqsrc}

@@

\label{sect:omega-notation2}
\begin{Coqsrc}
Notation omega := (ocons (ocons zero 0 zero) 0 zero).
\end{Coqsrc}

@@

\begin{Coqsrc}
Notation "'phi0' alpha" := (ocons alpha 0 zero) (at level 29) : t1_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Fixpoint omega_tower (height:nat) : T1 := 
 match height with 
 | 0 =>  1 
 | S h => phi0 (omega_tower h)
 end.
\end{Coqsrc}

@@

>>>>

\input{movies/snippets/T1/T1Def}

\paragraph{Remark}
The name \texttt{T1} we gave to this data-type  is proper to this development and refers
to a hierarchy of ordinal notations. For instance, in Library \href{../theories/html/hydras.Gamma0.T2.html}{Gamma0.T2},  the following type is used to represent ordinals strictly less than \(\Gamma_0\),  in Veblen normal form (see also~\cite{schutte}).
\noindent

\input{movies/snippets/T2/T2Def}

@@

\input{movies/snippets/T1/alpha0}

@@

@@

\input{movies/snippets/T1/finiteOrds}

@@

\label{sect:omega-notation2}

\input{movies/snippets/T1/omegaDef}

@@

\input{movies/snippets/T1/phi0Def}

@@

\input{movies/snippets/T1/towerDef}

@@

% Uncomment for testing 
%\textbf{Todo: Fix subgoal display }
%\input{movies/snippets/T1/compareRev}
